Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-14 analysis/sim/run_simpw.Rmd
png

par(mfrow=c(1,3))
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="index")
text((1:6*1.18)-0.38,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="index")
text((1:6*1.18)-0.38,rec+0.02,labels=signif(rec,3))

barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="index")
text((1:6*1.18)-0.38,f1+0.02,labels=signif(f1,3))

>>>>

par(mfrow=c(1,3))
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))

png("fig3_bars.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))
dev.off()
